\section{Software System Attributes}

\subsection{Reliability and Availability}
The application should  be tested so that reliability is not a problem and user do not experience any kind of error or interruption.

The application should have high availability and users should be able to rely on this application.
The system should have a 99.8\% of uptime.

The application should make use of a caching system so that in case of system or network failure users will still be able to access to data stored offline.

\subsection{Security}
All the communications between clients and the server will be encrypted and protected, thanks to the Firebase protocols.

All the information will be stored on the Firebase database and security will have high priority. All sensbile data will be encrypted,
and as login and authentication will be performed through Google accounts, passwords and other user credentials will not be a concern.

\subsection{Maintainability}
During the design of the application, maintainability was taken in consideration and the application should have good maintainability and low code complexity.

The code should be well documented following the Dart Language documentation instructions, so that other developers can easily understand it.

The source code management should be done through a Version Control System.


\subsection{Portability}
The application should run on any Android and iOS smartphone or 
tablet that satisfies the software and hardware requirements.

\subsection{Internationalization}
The application should be internationalized and support multiple languages.

It should adapt to the system language or, if the language is not supported, it should use English as default.